Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2023-01-11 edubots_surveys.Rnw
Update edubots_surveys.Rnw
Co-authored-by: Francisco Barranco <fbarranco@ugr.es>

Based on the discussion of this study, we propose here a potential process for
introducing technology that would need to be piloted in order to determine its
value and its relationship to improved learning outcomes and higher teacher
staff satisfaction.

>>>>

Based on the discussion of this study, we propose here a potential process for
introducing technology that would need to be piloted in order to determine its
value and its relationship to improved learning outcomes and higher teaching
staff satisfaction.
